```{r, libraries used}
  if(!require(rlang)){install.packages("rlang")}
  library(rlang)
  if(!require(piecewiseSEM)){install.packages("piecewiseSEM")}
  library(piecewiseSEM)
  if(!require(nlme)){install.packages("nlme")}
  library(nlme)
  if(!require(readxl)){install.packages("readxl")}
  library(readxl)
  if(!require(dplyr)){install.packages("dplyr")}
  library(dplyr)
  if(!require(mixtools)){install.packages("mixtools")}
  library(mixtools)
  if(!require(emmeans)){install.packages("emmeans")}
  library(emmeans)
  if(!require(readr)){install.packages("readr")}
  library(readr)
  if(!require(tidyverse)){install.packages("tidyverse")}
  library(tidyverse)
  if(!require(data.table)){install.packages("data.table")}
  library(data.table)
  if(!require(lubridate)){install.packages("lubridate")}
  library(lubridate)
  if(!require(ggplot2)){install.packages("ggplot2")}
  library(ggplot2)
  if(!require(ggpubr)){install.packages("ggpubr")}
  library(ggpubr)
  if(!require(rstatix)){install.packages("rstatix")}
  library(rstatix)
  if(!require(multcompView)){install.packages("multcompView")}
  library(multcompView)
  if(!require(knitr)){install.packages("knitr")}
  library(knitr)
  if(!require(DT)){install.packages("DT")}
  library(DT)
  if(!require(extrafont)){install.packages("extrafont")}
  library(extrafont)
  if(!require(easycsv)){install.packages("easycsv")}
  library(easycsv)
  if(!require(PairedData)){install.packages("PairedData")}
  library(PairedData)
  if(!require(compare)){install.packages("compare")}
  library(compare)
  if(!require(pastecs)){install.packages("pastecs")}
  library(pastecs)
  if(!require(pwr)){install.packages("pwr")}
  library(pwr)
  if(!require(gdata)){install.packages("gdata")}
  library(gdata)
  if(!require(skimr)){install.packages("skimr")}
  library(skimr)
  if(!require(summarytools)){install.packages("summarytools")}
  library(summarytools)
  if(!require(GGally)){install.packages("GGally")}
  library(GGally)
  if(!require(BSDA)){install.packages("BSDA")}
  library(BSDA)
  if(!requireNamespace("BiocManager", quietly = TRUE))
    if(!require(BiocManager)){install.packages("BiocManager")}
  if(!require(ggforce)){install.packages("ggforce")}
  library(ggforce)
  if(!require(svglite)){install.packages("svglite")}
  library(svglite)
  if(!require(devtools)) install.packages("devtools")
  if(!require(factoextra)){install.packages("factoextra")}
  library(factoextra)
  if(!require(mice)){install.packages("mice")}
  library(mice)
  if(!require(miceadds)){install.packages("miceadds")}
  library(miceadds)
  if(!require(micemd)){install.packages("micemd")}
  library(micemd)
  if(!require(ggmice)){install.packages("ggmice")}
  library(ggmice)
  if(!require(missForest)){install.packages("missForest")}
  library(missForest)
  if(!require(Hmisc)){install.packages("Hmisc")}
  library(Hmisc)
  if(!require(kableExtra)){install.packages("kableExtra")}
  library(kableExtra)
  if(!require(gt)){install.packages("gt")}
  library(gt)
  if(!require(glue)){install.packages("glue")}
  library(glue)
  if(!require(lmerTest)){install.packages("lmerTest")}
  library(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
  if(!require(effects)){install.packages("effects")}
  library(effects)
  if(!require(multilevelTools)){install.packages("multilevelTools")}
  library(multilevelTools)
  if(!require(RColorBrewer)){install.packages("RColorBrewer")}
  library(RColorBrewer)
  #note that gamlss masks functions from mfp and from lmer, so need to be careful
  if(!require(gamlss)){install.packages("gamlss")}
  library(gamlss)
  if(!require(lme4)){install.packages("lme4")}
  library(lme4)
  if(!require(mfp)){install.packages("mfp")}
  library(mfp)
  if(!require(glmnet)){install.packages("glmnet")}
  library(glmnet)
  if(!require(shrink)){install.packages("shrink_1.2.1.tar.gz", repos=NULL, type="source")}
  library(shrink)
  if(!require(slm)){install.packages("slm")}
  library(slm)
  if(!require(cowplot)){install.packages("cowplot")}
  library(cowplot)
  if(!require(lqmm)){install.packages("lqmm")}
  library(lqmm)
  if(!require(gridExtra)){install.packages("gridExtra")}
  library(gridExtra)
  if(!require(mice)){install.packages("mice")}
  library(mice)
  if(!require(tidyr)){install.packages("tidyr")}
  library(tidyr)
  if(!require(tibble)){install.packages("tibble")}
  library(tibble)
  if(!require(summarytools)){install.packages("summarytools")}
  library(summarytools)
  if(!require(childsds)){install.packages("childsds")}
  library(childsds)
  if(!require(pedbp)){install.packages("pedbp")}
  library(pedbp)
  if(!require(brms)){install.packages("brms")}
  library(brms)

#please note, not all libraries listed above were used 
```


```{r, data statement}
#to access data within the I-CAH registry, please apply at https://registry.i-dsd.org/user/login
#the data used for this analysis cannot be shared without an appropriate data sharing agreement
```

```{r, subset data and summary statistics of cohort}
bp_data_young_adult <-
  subset(bp_data, 
         age_to_use >20 & age_to_use <40)

bp_data_young_adult_male <- 
  subset(bp_data_young_adult,
         Sex.at.birth...Birth=="Male")

bp_data_young_adult_fema <- 
  subset(bp_data_young_adult,
         Sex.at.birth...Birth=="Female")

bp_data_young_adult_one_visit <-
  bp_data_young_adult %>%
  group_by(id) %>% 
  slice_max(age_to_use, with_ties = F)

cat("Number of rows")
nrow(bp_data_young_adult)
cat("Number of patients")
length(unique(bp_data_young_adult$id))
cat("Number of rows male")
nrow(bp_data_young_adult_male)
cat("Number of patients male")
length(unique(bp_data_young_adult_male$id))
cat("Number of rows fema")
nrow(bp_data_young_adult_fema)
cat("Number of patients fema")
length(unique(bp_data_young_adult_fema$id))
cat("Frequency of sex id")
freq(bp_data_young_adult_one_visit$Sex.at.birth...Birth)
cat("Frequency of sex visit")
freq(bp_data_young_adult$Sex.at.birth...Birth)
cat("Number of centres")
nrow(as.data.frame(freq(bp_data_young_adult$Centre.Name...Centre)))-2
cat("Frequency of centres")
freq(bp_data_young_adult$Centre.Name...Centre)

descr(bp_data_young_adult$interpolated_weight)
descr(bp_data_young_adult$interpolated_height)
descr(bp_data_young_adult$systolic_imputation_1)
#descr(bp_data_young_adult$totaltotal_daily_fludro_dose_carried_to_use_with_zero)
descr(bp_data_young_adult$total_daily_hydrocortisone_equivalent_at_visit)

descr(bp_data_young_adult_male$interpolated_weight)
descr(bp_data_young_adult_male$age_to_use)
descr(bp_data_young_adult_fema$interpolated_weight)
descr(bp_data_young_adult_fema$age_to_use)

freq(bp_data_young_adult_male$Hypertension...Comorbid.Conditions.and.Surgery)
freq(bp_data_young_adult_fema$Hypertension...Comorbid.Conditions.and.Surgery)
freq(bp_data_young_adult_one_visit$Hypertension...Comorbid.Conditions.and.Surgery)
```

```{r, multilevel quantile regression of systolic blood pressure with age and sex}
library(lqmm)
bp_data_young_adult_with_systolic <- 
  subset(bp_data_young_adult, !is.na(systolic_imputation_1))
systolic_lqmm_fit <- 
  lqmm::lqmm(fixed = systolic_imputation_1 ~
               age_to_use + 
               Sex.at.birth...Birth, 
                  random = ~1, 
                  group = id, 
                  tau = c(
                    #0.01, 
                    #0.05, 
                    0.1, 
                    0.5, 
                    0.9#, 
                    #0.95, 
                    #0.99
                    ), 
                  nK = 11, 
                  type = "normal", 
                  data = bp_data_young_adult_with_systolic)

summary(systolic_lqmm_fit)
```

```{r, plot systolic overall fit}
individual_line_width_peripheral <- 0.8
individual_line_width_central <- 1.8
individual_alpha_lines <- 0.4
individual_alpha_points <- 0.8
individual_size_points <- 0.8
peripheral_line_type <- "longdash"

fitted_values <- 
  as.data.frame(predict(systolic_lqmm_fit))
colnames(fitted_values) <- 
  paste0("systolic_lqmm_fit_", colnames(fitted_values))

bp_data_young_adult_with_systolic_with_fit <-
  cbind(bp_data_young_adult_with_systolic,
        fitted_values)

systolic_lqmm_plot <-
  ggplot(bp_data_young_adult_with_systolic_with_fit,
        aes(x = age_to_use,
            colour=Sex.at.birth...Birth)
       ) +
  geom_line( 
       aes(y = systolic_lqmm_fit_0.1),
       linewidth=individual_line_width_peripheral,
       alpha=individual_alpha_lines,
       linetype=peripheral_line_type) +
  geom_line( 
       aes(y = systolic_lqmm_fit_0.5),
       linewidth=individual_line_width_central,
       alpha=individual_alpha_lines) +
  geom_line( 
       aes(y = systolic_lqmm_fit_0.9),
       linewidth=individual_line_width_peripheral,
       alpha=individual_alpha_lines,
       linetype=peripheral_line_type) +
  geom_point(
    aes(y=systolic_imputation_0),
    size=individual_size_points,
    alpha=individual_alpha_points
  ) +
  labs(title = "LQMM Fitted Lines for Different Quantiles",
       x = "Age (years)",
       y = "Systolic blood pressure (mmHg)") +
  scale_color_manual(values = c("Male" = "blue", "Female" = "red")) +
  scale_y_continuous(
      limits=c(90,160),
  breaks=c(seq(90,160, by=10)))+

  themepowerpoint
systolic_lqmm_plot
ggsave(file="./systolic_lqmm_plot.tif",
       plot=systolic_lqmm_plot, 
       device="tiff", 
       width=10, height=5 , 
       compression = "lzw")

```

```{r, 5th centiles and 95th centiles}
#systolic 5th:
#tau = 0.05##
#
#Fixed effects:
#                             Value Std. Error lower bound upper bound  Pr(>|t|)    
#(Intercept)              116.36685    4.45203   107.42015    125.3135 < 2.2e-16 ***
#age_to_use                -0.55075    0.18432    -0.92116     -0.1803 0.0043791 ** 
#Sex.at.birth...BirthMale   7.76969    1.97017     3.81047     11.7289 0.0002552 ***
#  
#systolic 95th  
#tau = 0.95#

#Fixed effects:
#                              Value Std. Error lower bound upper bound  Pr(>|t|)    
#(Intercept)              117.774549   4.429932  108.872266    126.6768 < 2.2e-16 ***
#age_to_use                 0.455569   0.194730    0.064246      0.8469   0.02343 *  
#Sex.at.birth...BirthMale   9.130401   2.065561    4.979501     13.2813  5.46e-05 ***  
#  
#diastolic 5th:#
#tau = 0.05

#Fixed effects:
#                            Value Std. Error lower bound upper bound Pr(>|t|)    
#(Intercept)              65.89296    3.33380    59.19344     72.5925  < 2e-16 ***
#age_to_use               -0.21589    0.11166    -0.44028      0.0085  0.05897 .  
#Sex.at.birth...BirthMale  3.32309    1.36659     0.57682      6.0694  0.01873 *  
#  
#diastolic 95th:
#tau = 0.95#

#Fixed effects:
#                            Value Std. Error lower bound upper bound  Pr(>|t|)    
#(Intercept)              67.13595    3.28065    60.54324     73.7287 < 2.2e-16 ***
#age_to_use                0.68333    0.13180     0.41847      0.9482 4.094e-06 ***
#Sex.at.birth...BirthMale  4.85816    1.35296     2.13929      7.5770 0.0007617 ***
  
print("Girls at age 20 will be systolic range between 5th and 95th of:")
(117.774549 + 20 * 0.455569) - (116.36685 + 20 * -0.55075)
print("Girls at age 20 will be diastolic range between 5th and 95th of:")
(67.13595 + 0.68333 * 20) - (65.89296 + -0.21589 * 20)

  
print("Girls at age 40 will be systolic range between 5th and 95th of:")
(117.774549 + 40 * 0.455569) - (116.36685 + 40 * -0.55075)
print("Girls at age 40 will be diastolic  range between 5th and 95th of:")
(67.13595 + 0.68333 * 40) - (65.89296 + -0.21589 * 40)

cat("******************")
  
print("Boys will be the same range because we've just done a random intercept model")
```


```{r, multilevel quantile regression of diastolic blood pressure with age and sex}

bp_data_young_adult_with_diastolic <- 
  subset(bp_data_young_adult, !is.na(diastolic_imputation_1))

diastolic_lqmm_fit <- 
  lqmm::lqmm(fixed = 
             diastolic_imputation_1 ~ 
             age_to_use + 
             Sex.at.birth...Birth, 
                  random = ~1, 
                  group = id, 
                  tau = c(
                    #0.01, 
                    #0.05, 
                    0.1, 
                    0.5, 
                    0.9#, 
                    #0.95, 
                    #0.99
                    ), 
                  nK = 11, 
                  type = "normal", 
                  data = bp_data_young_adult_with_diastolic)

summary(diastolic_lqmm_fit)
```


```{r, plot diastolic overall fit}
individual_line_width_peripheral <- 0.8
individual_line_width_central <- 1.8
individual_alpha_lines <- 0.4
individual_alpha_points <- 0.8
individual_size_points <- 0.8
peripheral_line_type <- "longdash"

fitted_values <- 
  as.data.frame(predict(diastolic_lqmm_fit))
colnames(fitted_values) <- paste0("diastolic_lqmm_fit_", colnames(fitted_values))

bp_data_young_adult_with_diastolic_with_fit <-
  cbind(bp_data_young_adult_with_diastolic,
        fitted_values)
diastolic_lqmm_plot <-
  ggplot(bp_data_young_adult_with_diastolic_with_fit,
        aes(x = age_to_use,
            colour=Sex.at.birth...Birth)
       ) +
  geom_line( 
       aes(y = diastolic_lqmm_fit_0.1),
       linewidth=individual_line_width_peripheral,
       alpha=individual_alpha_lines,
       linetype=peripheral_line_type) +
  geom_line( 
       aes(y = diastolic_lqmm_fit_0.5),
       linewidth=individual_line_width_central,
       alpha=individual_alpha_lines) +
  geom_line( 
       aes(y = diastolic_lqmm_fit_0.9),
       linewidth=individual_line_width_peripheral,
       alpha=individual_alpha_lines,
       linetype=peripheral_line_type) +
  geom_point(
    aes(y=diastolic_imputation_0),
    size=individual_size_points,
    alpha=individual_alpha_points
  ) +
  labs(title = "LQMM Fitted Lines for Different Quantiles",
       x = "Age (years)",
       y = "Diastolic blood pressure (mmHg)") +
  scale_color_manual(values = c("Male" = "blue", "Female" = "red")) +
  scale_y_continuous(
      limits=c(50,120),
      breaks=c(seq(50,120, by=10)))+
  themepowerpoint
diastolic_lqmm_plot
ggsave(file="./diastolic_lqmm_plot.tif",
       plot=diastolic_lqmm_plot, 
       device="tiff", 
       width=10, height=5 , 
       compression = "lzw")

```



```{r, multilevel quantile regression of diastolic blood pressure with age and sex}
#new_data <- 
#  data.frame(age_to_use=30,
#             Sex.at.birth...Birth="Male",
#             id=99999)
#
#a <- predict(systolic_lqmm_fit, 
#             newdata = new_data,
#             level = 0)
#tau = 0.5
#50th centile results:
#Fixed effects:
#                             Value Std. Error lower bound upper bound  Pr(>|t|)    
#(Intercept)              116.95026    5.03501   106.83202    127.0685 < 2.2e-16 ***
#age_to_use                -0.12090    0.16939    -0.46130      0.2195    0.4788    
#Sex.at.birth...BirthMale   9.28055    2.04537     5.17023     13.3909 3.702e-05 ***



#Fixed effects:
#                            Value Std. Error lower bound upper bound  Pr(>|t|)    
#(Intercept)              67.30351    3.37066    60.52991     74.0771 < 2.2e-16 ***
#age_to_use                0.14755    0.12107    -0.09574      0.3908  0.228767    
#Sex.at.birth...BirthMale  4.63254    1.47732     1.66375      7.6013  0.002896 ** 

print("Female imputed 1 systolic goes from this at 20")  
116.95026 + 0.12090 * 20
print("Female imputed 1 diastolic goes from this at 20")  
67.30351 + 0.14755 * 20
print("******")
print("Female imputed 1 systolic goes from to this at 40")  
116.95026 + 0.12090 * 40
print("Female imputed 1 diastolic goes from to this at 40")  
67.30351 + 0.14755 * 40
print("******")
print("Male imputed 1 systolic goes from this at 20")  
116.95026 + 0.12090 * 20 + 9.28055
print("Male imputed 1 diastolic goes from this at 20")  
67.30351 + 0.14755 * 20 + 4.63254
print("******")
print("Male imputed 1 systolic goes from to this at 40")  
116.95026 + 0.12090 * 40 + 9.28055
print("Male imputed 1 diastolic goes from to this at 40")  
67.30351 + 0.14755 * 40 + 4.63254
  
print("Report the numbers at age 30:")

print("Female imputed 1 systolic goes from this at 30")  
116.95026 + 0.12090 * 30
print("Female imputed 1 diastolic goes from this at 30")  
67.30351 + 0.14755 * 30
print("******")
print("Male imputed 1 systolic goes from to this at 30")  
116.95026 + 0.12090 * 30 + 9.28055
print("Male imputed 1 diastolic goes from to this at 30")  
67.30351 + 0.14755 * 30 + 4.63254
```

#########################################
Systolic models with covariates
#########################################


```{r, fit multilevel_with_age_and_sex systolic}
multilevel_with_age_and_sex_systolic <-
  lmer(data = 
         bp_data_young_adult,
   formula = 
     systolic_imputation_1 ~
     age_to_use +
     Sex.at.birth...Birth +
     (1 | id) + (1 | Centre.Name...Centre) )
summary_multilevel_with_age_and_sex_systolic <- summary(multilevel_with_age_and_sex_systolic)
multilevel_with_age_and_sex_systolic_age_estimate <-
  summary_multilevel_with_age_and_sex_systolic$coefficients["age_to_use", "Estimate"]
multilevel_with_age_and_sex_systolic_age_stderr <-
  summary_multilevel_with_age_and_sex_systolic$coefficients["age_to_use", "Std. Error"]
multilevel_with_age_and_sex_systolic_r_squared <-
  rsquared(multilevel_with_age_and_sex_systolic)$Conditional
```


```{r, fit multilevel_with_age_and_weight systolic}
multilevel_with_age_and_weight_systolic <-
  lmer(data = 
         bp_data_young_adult,
   formula = 
     systolic_imputation_1 ~
     age_to_use +
     interpolated_weight +
     Sex.at.birth...Birth +
     (1 | id) + (1 | Centre.Name...Centre) )
summary_multilevel_with_age_and_weight_systolic <- summary(multilevel_with_age_and_weight_systolic)
multilevel_with_age_and_weight_systolic_age_estimate <-
  summary_multilevel_with_age_and_weight_systolic$coefficients["age_to_use", "Estimate"]
multilevel_with_age_and_weight_systolic_age_stderr <-
  summary_multilevel_with_age_and_weight_systolic$coefficients["age_to_use", "Std. Error"]
multilevel_with_age_and_weight_systolic_weight_estimate <-
  summary_multilevel_with_age_and_weight_systolic$coefficients["interpolated_weight", "Estimate"]
multilevel_with_age_and_weight_systolic_weight_stderr <-
  summary_multilevel_with_age_and_weight_systolic$coefficients["interpolated_weight", "Std. Error"]
multilevel_with_age_and_weight_systolic_r_squared <-
  rsquared(multilevel_with_age_and_weight_systolic)$Conditional
```


```{r, multilevel_with_age_and_weight_and_fludro systolic}
multilevel_with_age_and_weight_and_fludro_systolic <-
  lmer(data = 
         bp_data_young_adult,
   formula = 
     systolic_imputation_1 ~
     age_to_use +
     interpolated_weight +
     Sex.at.birth...Birth +
     total_daily_hydrocortisone_equivalent_at_visit +
     total_daily_fludro_dose_carried_to_use_with_zero +
     (1 | id) + (1 | Centre.Name...Centre) )
summary_multilevel_with_age_and_weight_and_fludro_systolic <-
  summary(multilevel_with_age_and_weight_and_fludro_systolic)

multilevel_with_age_and_weight_and_fludro_systolic_age_estimate <-
  summary_multilevel_with_age_and_weight_and_fludro_systolic$coefficients[
    "age_to_use", "Estimate"]
multilevel_with_age_and_weight_and_fludro_systolic_age_stderr <-
  summary_multilevel_with_age_and_weight_and_fludro_systolic$coefficients[
    "age_to_use", "Std. Error"]

multilevel_with_age_and_weight_and_fludro_systolic_weight_estimate <-
  summary_multilevel_with_age_and_weight_and_fludro_systolic$coefficients[
    "interpolated_weight", "Estimate"]
multilevel_with_age_and_weight_and_fludro_systolic_weight_stderr <-
  summary_multilevel_with_age_and_weight_and_fludro_systolic$coefficients[
    "interpolated_weight", "Std. Error"]

multilevel_with_age_and_weight_and_fludro_systolic_hydro_estimate <-
  summary_multilevel_with_age_and_weight_and_fludro_systolic$coefficients[
    "total_daily_hydrocortisone_equivalent_at_visit", "Estimate"]
multilevel_with_age_and_weight_and_fludro_systolic_hydro_stderr <-
  summary_multilevel_with_age_and_weight_and_fludro_systolic$coefficients[
    "total_daily_hydrocortisone_equivalent_at_visit", "Std. Error"]

multilevel_with_age_and_weight_and_fludro_systolic_fludro_estimate <-
  summary_multilevel_with_age_and_weight_and_fludro_systolic$coefficients[
    "total_daily_fludro_dose_carried_to_use_with_zero", "Estimate"]
multilevel_with_age_and_weight_and_fludro_systolic_fludro_stderr <-
  summary_multilevel_with_age_and_weight_and_fludro_systolic$coefficients[
    "total_daily_fludro_dose_carried_to_use_with_zero", "Std. Error"]

multilevel_with_age_and_weight_and_fludro_systolic_r_squared <-
  rsquared(multilevel_with_age_and_weight_and_fludro_systolic)$Conditional
```

#########################################
diastolic models with covariates
#########################################


```{r, fit multilevel_with_age_and_sex diastolic}
multilevel_with_age_and_sex_diastolic <-
  lmer(data = 
         bp_data_young_adult,
   formula = 
     diastolic_imputation_1 ~
     age_to_use +
     Sex.at.birth...Birth +
     (1 | id) + (1 | Centre.Name...Centre) )
summary_multilevel_with_age_and_sex_diastolic <- summary(multilevel_with_age_and_sex_diastolic)
multilevel_with_age_and_sex_diastolic_age_estimate <-
  summary_multilevel_with_age_and_sex_diastolic$coefficients["age_to_use", "Estimate"]
multilevel_with_age_and_sex_diastolic_age_stderr <-
  summary_multilevel_with_age_and_sex_diastolic$coefficients["age_to_use", "Std. Error"]
multilevel_with_age_and_sex_diastolic_r_squared <-
  rsquared(multilevel_with_age_and_sex_diastolic)$Conditional
```


```{r, fit multilevel_with_age_and_weight diastolic}
multilevel_with_age_and_weight_diastolic <-
  lmer(data = 
         bp_data_young_adult,
   formula = 
     diastolic_imputation_1 ~
     age_to_use +
     interpolated_weight +
     Sex.at.birth...Birth +
     (1 | id) + (1 | Centre.Name...Centre) )
summary_multilevel_with_age_and_weight_diastolic <- 
  summary(multilevel_with_age_and_weight_diastolic)
multilevel_with_age_and_weight_diastolic_age_estimate <-
  summary_multilevel_with_age_and_weight_diastolic$coefficients["age_to_use", "Estimate"]
multilevel_with_age_and_weight_diastolic_age_stderr <-
  summary_multilevel_with_age_and_weight_diastolic$coefficients["age_to_use", "Std. Error"]
multilevel_with_age_and_weight_diastolic_weight_estimate <-
  summary_multilevel_with_age_and_weight_diastolic$coefficients["interpolated_weight", "Estimate"]
multilevel_with_age_and_weight_diastolic_weight_stderr <-
  summary_multilevel_with_age_and_weight_diastolic$coefficients["interpolated_weight", "Std. Error"]
multilevel_with_age_and_weight_diastolic_r_squared <-
  rsquared(multilevel_with_age_and_weight_diastolic)$Conditional
```


```{r, multilevel_with_age_and_weight_and_fludro diastolic}
multilevel_with_age_and_weight_and_fludro_diastolic <-
  lmer(data = 
         bp_data_young_adult,
   formula = 
     diastolic_imputation_1 ~
     age_to_use +
     interpolated_weight +
     Sex.at.birth...Birth +
     total_daily_hydrocortisone_equivalent_at_visit +
     total_daily_fludro_dose_carried_to_use_with_zero +
     (1 | id) + (1 | Centre.Name...Centre) )
summary_multilevel_with_age_and_weight_and_fludro_diastolic <-
  summary(multilevel_with_age_and_weight_and_fludro_diastolic)
multilevel_with_age_and_weight_and_fludro_diastolic_age_estimate <-
  summary_multilevel_with_age_and_weight_and_fludro_diastolic$coefficients[
    "age_to_use", "Estimate"]
multilevel_with_age_and_weight_and_fludro_diastolic_age_stderr <-
  summary_multilevel_with_age_and_weight_and_fludro_diastolic$coefficients[
    "age_to_use", "Std. Error"]
multilevel_with_age_and_weight_and_fludro_diastolic_weight_estimate <-
  summary_multilevel_with_age_and_weight_and_fludro_diastolic$coefficients[
    "interpolated_weight", "Estimate"]
multilevel_with_age_and_weight_and_fludro_diastolic_weight_stderr <-
  summary_multilevel_with_age_and_weight_and_fludro_diastolic$coefficients[
    "interpolated_weight", "Std. Error"]
multilevel_with_age_and_weight_and_fludro_diastolic_hydro_estimate <-
  summary_multilevel_with_age_and_weight_and_fludro_diastolic$coefficients[
    "total_daily_hydrocortisone_equivalent_at_visit", "Estimate"]
multilevel_with_age_and_weight_and_fludro_diastolic_hydro_stderr <-
  summary_multilevel_with_age_and_weight_and_fludro_diastolic$coefficients[
    "total_daily_hydrocortisone_equivalent_at_visit", "Std. Error"]
multilevel_with_age_and_weight_and_fludro_diastolic_fludro_estimate <-
  summary_multilevel_with_age_and_weight_and_fludro_diastolic$coefficients[
    "total_daily_fludro_dose_carried_to_use_with_zero", "Estimate"]
multilevel_with_age_and_weight_and_fludro_diastolic_fludro_stderr <-
  summary_multilevel_with_age_and_weight_and_fludro_diastolic$coefficients[
    "total_daily_fludro_dose_carried_to_use_with_zero", "Std. Error"]

multilevel_with_age_and_weight_and_fludro_diastolic_r_squared <-
  rsquared(multilevel_with_age_and_weight_and_fludro_diastolic)$Conditional
```

*****************************************

Visualisations

*****************************************




ESPE 2024 abstract said:

Multivariable LMEM showed that an increase in weight had a significant effect on systolic (estimate=0.2, standard error (SE)=0.05, p<0.001, R2cond=0.44) and diastolic (estimate=0.1, SE=0.04, p=0.02, R2cond=0.29) blood pressure, whereas the models showed an insignificant effect of either hydrocortisone or fludrocortisone dosing (p>0.05).

To display this we plot the weight coefficient, hydrocortisone coefficient and fludrocortisone coefficient for both systolic and diastolic

i.e. plot
multilevel_with_age_and_weight_and_fludro_systolic_weight_estimate
multilevel_with_age_and_weight_and_fludro_systolic_weight_stderr

multilevel_with_age_and_weight_and_fludro_systolic_hydro_estimate
multilevel_with_age_and_weight_and_fludro_systolic_hydro_stderr

multilevel_with_age_and_weight_and_fludro_systolic_fludro_estimate
multilevel_with_age_and_weight_and_fludro_systolic_fludro_stderr

```{r, plot of effect sizes}
effect_size_data <-
  data.frame(
    metric=c(
  "Weight_sys_mean",
  "Fludro_sys_mean",
  "Hydro_sys_mean",
  "Weight_dias_mean",
  "Fludro_dias_mean",
  "Hydro_dias_mean"),
    position=c(
    "Weight_sys",
    "Fludro_sys",
    "Hydro_sys",
    "Weight_dias",
    "Fludro_dias",
    "Hydro_dias"),
  value=c(multilevel_with_age_and_weight_and_fludro_systolic_weight_estimate,
          
          multilevel_with_age_and_weight_and_fludro_systolic_fludro_estimate,
          
          multilevel_with_age_and_weight_and_fludro_systolic_hydro_estimate,
          
          multilevel_with_age_and_weight_and_fludro_diastolic_weight_estimate,
          
          multilevel_with_age_and_weight_and_fludro_diastolic_fludro_estimate,
          
          multilevel_with_age_and_weight_and_fludro_diastolic_hydro_estimate
          
           ))

#extract a column for systolic or diastolic
effect_size_data$cardiac_cycle <-
  ifelse(grepl(x=effect_size_data$metric,
               pattern="sys"),
         "systole",
         "diastole")

confidence_intervals <-
  data.frame(
    metric=c(
      "Weight_sys",
      "Fludro_sys",
      "Hydro_sys",
      "Weight_dias",
      "Fludro_dias",
      "Hydro_dias"
    ),
    
    lower=c(
          multilevel_with_age_and_weight_and_fludro_systolic_weight_estimate - 
            1.96 * multilevel_with_age_and_weight_and_fludro_systolic_weight_stderr,
          multilevel_with_age_and_weight_and_fludro_systolic_fludro_estimate - 
            1.96 * multilevel_with_age_and_weight_and_fludro_systolic_fludro_stderr,
          multilevel_with_age_and_weight_and_fludro_systolic_hydro_estimate - 
            1.96 * multilevel_with_age_and_weight_and_fludro_systolic_hydro_stderr,
          
          multilevel_with_age_and_weight_and_fludro_diastolic_weight_estimate - 
            1.96 * multilevel_with_age_and_weight_and_fludro_diastolic_weight_stderr,
          multilevel_with_age_and_weight_and_fludro_diastolic_fludro_estimate - 
            1.96 * multilevel_with_age_and_weight_and_fludro_diastolic_fludro_stderr,
          multilevel_with_age_and_weight_and_fludro_diastolic_hydro_estimate - 
            1.96 * multilevel_with_age_and_weight_and_fludro_diastolic_hydro_stderr
        
    ),
    
    upper=c(
          multilevel_with_age_and_weight_and_fludro_systolic_weight_estimate + 
            1.96 * multilevel_with_age_and_weight_and_fludro_systolic_weight_stderr,
          multilevel_with_age_and_weight_and_fludro_systolic_fludro_estimate + 
            1.96 * multilevel_with_age_and_weight_and_fludro_systolic_fludro_stderr,
          multilevel_with_age_and_weight_and_fludro_systolic_hydro_estimate + 
            1.96 * multilevel_with_age_and_weight_and_fludro_systolic_hydro_stderr,
          
          multilevel_with_age_and_weight_and_fludro_diastolic_weight_estimate + 
            1.96 * multilevel_with_age_and_weight_and_fludro_diastolic_weight_stderr,
          multilevel_with_age_and_weight_and_fludro_diastolic_fludro_estimate + 
            1.96 * multilevel_with_age_and_weight_and_fludro_diastolic_fludro_stderr,
          multilevel_with_age_and_weight_and_fludro_diastolic_hydro_estimate + 
            1.96 * multilevel_with_age_and_weight_and_fludro_diastolic_hydro_stderr
        
    )
  )

#extract a column for systolic or diastolic
confidence_intervals$cardiac_cycle <-
  ifelse(grepl(x=confidence_intervals$metric,
               pattern="sys"),
         "systole",
         "diastole")

#to just give a basic visualisation for a poster
effect_size_plot <-
  ggplot(data=effect_size_data) +
  geom_hline(yintercept=0, 
             colour="black", 
             linewidth=2,
             linetype="longdash") +
  geom_errorbar(data=confidence_intervals,
                aes(x=metric,
                     ymin=lower,
                     ymax=upper,
                colour=cardiac_cycle),
                width=.6,
                linewidth=2) +
  labs(x=NULL,
       y=NULL) +
  scale_colour_manual(
    values = c(
    "systole" = "purple",
    "diastole" = "orange")) +
  geom_point(
    data=subset(effect_size_data,
                  metric=="Weight_sys_mean" |
                  metric=="Fludro_sys_mean" |
                  metric=="Hydro_sys_mean" |
                  metric=="Weight_dias_mean" |
                  metric=="Fludro_dias_mean" |
                  metric=="Hydro_dias_mean"),
    aes(x=position, 
        y=value,
        colour=cardiac_cycle),
    size=12,
    shape="square") +
  coord_flip() +
  themepowerpoint

effect_size_plot

ggsave(filename=paste0("effect_size_plot_for_young_adult_poster.tif"),
#       path=(), 
       plot = effect_size_plot, 
       device="tiff",  
       width=15, 
       height=4, 
       compression = "lzw", 
       limitsize=F)
```


```{r, total_daily_fludro_dose_carried_to_use_with_zero dot plot}
specific_stack_ratio <- 20
specific_dot_size <- 1.5

data_to_plot <- 
  bp_data_young_adult

mean_values <- data_to_plot %>%
  group_by(Sex.at.birth...Birth) %>%
  summarise(total_daily_fludro_dose_carried_to_use_with_zero  = 
              mean(total_daily_fludro_dose_carried_to_use_with_zero))
mean_values$x = c(0.5, 1.5)
mean_values$xend = c(1.5, 2.5)

summary_current_fludro <-
  ggplot(data=data_to_plot, 
         aes(colour=Sex.at.birth...Birth,
             x=Sex.at.birth...Birth, 
             y=total_daily_fludro_dose_carried_to_use_with_zero)) +
  #for geom_violin the alpha only affects the fill not the outline, so we hack to have a zero outline
  geom_violin(aes(fill=Sex.at.birth...Birth), alpha=0.1, linewidth=0) +
  geom_dotplot(
    aes(fill=Sex.at.birth...Birth),
    binwidth = 0.01,
    binaxis = "y", 
               stackdir = "center",
               stackratio = specific_stack_ratio,
               dotsize = specific_dot_size) +
  geom_segment(data=mean_values,
               aes(x = x, xend = xend, 
                   y = total_daily_fludro_dose_carried_to_use_with_zero , 
                   yend = total_daily_fludro_dose_carried_to_use_with_zero ,
                   colour=Sex.at.birth...Birth), 
               #size = 0.5, 
               linewidth=2,
               alpha = 0.4
) +
  labs(x=NULL,
       y=NULL) +
  scale_color_manual(values = c("Male" = "blue", "Female" = "red")) +
  scale_fill_manual(values = c("Male" = "blue", "Female" = "red")) +
  theme(panel.background = element_rect(fill="white",colour="azure2"), legend.position = "none",
                          panel.grid.major = element_line(colour="azure2") ,
                          axis.line.x.bottom = element_line(colour="black") ,
                          axis.line.y.left = element_line(colour="black") ,
                          plot.title = element_blank(),
                          plot.subtitle = element_text(size=9, hjust=0.5),
                          axis.text=element_text(size=6),
                          axis.title=element_text(size=6, face="bold"),
                          #change stuff for facet labels
                          strip.background =element_rect(fill="black", colour="black"),
                          strip.text = element_text(colour = 'white', size=6))

summary_current_fludro

dir.create("summary_dot_plots")
ggsave(filename=paste0("summary_current_fludro.tif"),
       path = ("summary_dot_plots"), 
       plot = summary_current_fludro, 
       device="tiff",  
       width=4, 
       height=4, 
       compression = "lzw", 
       limitsize=F)

```


```{r, total_daily_hydrocortisone_equivalent_at_visit dot plot}
specific_stack_ratio <- 20
specific_dot_size <- 1.5

data_to_plot <- 
  bp_data_young_adult

mean_values <- data_to_plot %>%
  group_by(Sex.at.birth...Birth) %>%
  summarise(total_daily_hydrocortisone_equivalent_at_visit  = 
              mean(total_daily_hydrocortisone_equivalent_at_visit, na.rm=T))
mean_values$x = c(0.5, 1.5)
mean_values$xend = c(1.5, 2.5)

summary_current_hydro <-
  ggplot(data=data_to_plot, 
         aes(colour=Sex.at.birth...Birth,
             x=Sex.at.birth...Birth, 
             y=total_daily_hydrocortisone_equivalent_at_visit)) +
  #for geom_violin the alpha only affects the fill not the outline, so we hack to have a zero outline
  geom_violin(aes(fill=Sex.at.birth...Birth), alpha=0.1, linewidth=0) +
  geom_dotplot(
    aes(fill=Sex.at.birth...Birth),
    binwidth = 0.01,
    binaxis = "y", 
               stackdir = "center",
               stackratio = specific_stack_ratio,
               dotsize = specific_dot_size) +
  geom_segment(data=mean_values,
               aes(x = x, xend = xend, 
                   y = total_daily_hydrocortisone_equivalent_at_visit , 
                   yend = total_daily_hydrocortisone_equivalent_at_visit ,
                   colour=Sex.at.birth...Birth), 
               #size = 0.5, 
               linewidth=2,
               alpha = 0.4
) +
  labs(x=NULL,
       y=NULL) +
  scale_color_manual(values = c("Male" = "blue", "Female" = "red")) +
  scale_fill_manual(values = c("Male" = "blue", "Female" = "red")) +
  theme(panel.background = element_rect(fill="white",colour="azure2"), legend.position = "none",
                          panel.grid.major = element_line(colour="azure2") ,
                          axis.line.x.bottom = element_line(colour="black") ,
                          axis.line.y.left = element_line(colour="black") ,
                          plot.title = element_blank(),
                          plot.subtitle = element_text(size=9, hjust=0.5),
                          axis.text=element_text(size=6),
                          axis.title=element_text(size=6, face="bold"),
                          #change stuff for facet labels
                          strip.background =element_rect(fill="black", colour="black"),
                          strip.text = element_text(colour = 'white', size=6))

summary_current_hydro

dir.create("summary_dot_plots")
ggsave(filename=paste0("summary_current_hydro.tif"),
       path = ("summary_dot_plots"), 
       plot = summary_current_hydro, 
       device="tiff",  
       width=4, 
       height=4, 
       compression = "lzw", 
       limitsize=F)

```


```{r, interpolated_weight dot plot}
specific_stack_ratio <- 100
specific_dot_size <- 1.5

data_to_plot <- 
  bp_data_young_adult

mean_values <- data_to_plot %>%
  group_by(Sex.at.birth...Birth) %>%
  summarise(interpolated_weight  = 
              mean(interpolated_weight, na.rm=T))
mean_values$x = c(0.5, 1.5)
mean_values$xend = c(1.5, 2.5)

summary_current_weight <-
  ggplot(data=data_to_plot, 
         aes(colour=Sex.at.birth...Birth,
             x=Sex.at.birth...Birth, 
             y=interpolated_weight)) +
  #for geom_violin the alpha only affects the fill not the outline, so we hack to have a zero outline
  geom_violin(aes(fill=Sex.at.birth...Birth), alpha=0.1, linewidth=0) +
  geom_dotplot(
    aes(fill=Sex.at.birth...Birth),
    binwidth = 0.01,
    binaxis = "y", 
               stackdir = "center",
               stackratio = specific_stack_ratio,
               dotsize = specific_dot_size) +
  geom_segment(data=mean_values,
               aes(x = x, xend = xend, 
                   y = interpolated_weight , 
                   yend = interpolated_weight ,
                   colour=Sex.at.birth...Birth), 
               #size = 0.5, 
               linewidth=2,
               alpha = 0.4
) +
  labs(x=NULL,
       y=NULL) +
  scale_color_manual(values = c("Male" = "blue", "Female" = "red")) +
  scale_fill_manual(values = c("Male" = "blue", "Female" = "red")) +
  theme(panel.background = element_rect(fill="white",colour="azure2"), legend.position = "none",
                          panel.grid.major = element_line(colour="azure2") ,
                          axis.line.x.bottom = element_line(colour="black") ,
                          axis.line.y.left = element_line(colour="black") ,
                          plot.title = element_blank(),
                          plot.subtitle = element_text(size=9, hjust=0.5),
                          axis.text=element_text(size=6),
                          axis.title=element_text(size=6, face="bold"),
                          #change stuff for facet labels
                          strip.background =element_rect(fill="black", colour="black"),
                          strip.text = element_text(colour = 'white', size=6))

summary_current_weight

dir.create("summary_dot_plots")
ggsave(filename=paste0("summary_current_weight.tif"),
       path = ("summary_dot_plots"), 
       plot = summary_current_weight, 
       device="tiff",  
       width=4, 
       height=4, 
       compression = "lzw", 
       limitsize=F)

```









